\vspace{-2.0cm} \textbf{A self supervised method to detect nouns and numbers in a non-annotated signs language corpus}

### 2023-07-03 articles/2021/self-supervised-method-to-detect-nouns-and-numbers/article-tesis.tex
updates to the paper introduction

In recent years, there has been a significant surge in interest surrounding inclusive software. The aim is to enhance accessibility and improve user experience. Incorporating inclusivity is essential to ensure seamless interaction between individuals with temporal or permanent physical limitations and computer systems. Deafness is a prevalent physical limitation, according to the World Health Organization (WHO), over 466 million people worldwide experience some level of hearing loss \cite{deafness_and_hearing_loss_2020} and approximately 8\% of the Peruvian population is affected by hearing loss \cite{disabilities_survey_2012}. Despite that there have been great advances on using AI for sign language recognition the lack of large annotated dataset and the complexity associated to learn intrinsic relations and dependencies between continuous sign languages constructions have posed challenges \cite{adaloglou2020comprehensive}. These challenges  have transformed the problem into a high dimensional problem that cannot be solved solely with supervision \cite{facebook-ssl}. Starting a model architecture design that leverages pre-trained models is always a good starting point even when using a ResNet50 pre-trained with ImageNet backbone, the resulting model will leverage a set of fine tuned layers decreasing time and data volume required for training. Previous knowledge and existing skill-sets are vital elements that will indeed decrease the teaching required to learn a new task. Yann Lecun have used an analogy where he compares the time and skills humans require to learn to drive a car with the massive amount of time and a data required to train autonomous cars emphasizing that previous knowledge and skillsets will greatly reduce training time as well as the data require to train a model \cite{facebook-ssl}.

>>>>

In recent years, there has been a significant surge in interest surrounding inclusive software. The aim is to enhance accessibility and improve user experience. Incorporating inclusivity is essential to ensure seamless interaction between individuals with temporal or permanent physical limitations and computer systems. Deafness is a prevalent physical limitation, according to the World Health Organization (WHO), over 466 million people worldwide experience some level of hearing loss \cite{deafness_and_hearing_loss_2020} and approximately 8\% of the Peruvian population is affected by hearing loss \cite{disabilities_survey_2012}. Despite that there have been great advances on using AI for sign languages recognition, the absence of large annotated dataset and the complexity associated to learn intrinsic relations and dependencies between continuous sign languages constructions have posed challenges \cite{adaloglou2020comprehensive}. These challenges  have transformed the problem into a high dimensional problem that cannot be solved solely with supervision \cite{facebook-ssl}. Starting a model architecture design that leverages pre-trained models is always a good starting point even when using a ResNet50 pre-trained with ImageNet backbone, the resulting model will leverage a set of fine tuned layers decreasing time and data volume required for training. Previous knowledge and existing skill-sets are vital elements that will indeed decrease the teaching required to learn a new task. Yann Lecun have used an analogy where he compares the time and skills humans require to learn to drive a car with the massive amount of time and a data required to train autonomous cars emphasizing that previous knowledge and skillsets will greatly reduce training time as well as the data require to train a model \cite{facebook-ssl}.
